% Allow relative paths in included subfiles that are compiled separately
% See https://tex.stackexchange.com/questions/153312/
\providecommand{\main}{..}
\documentclass[\main/thesis.tex]{subfiles}
\externaldocument{}



\begin{document}

\chapter{Datasets Details and Downloads}
\label{appendix:datasets}
\section{Download Instructions}
FreeDB, survey data, and randomly generated sounds can be downloaded from: \url{https://zenodo.org/record/3994999}\\
RadarDB requires lengthy downloads and processing. The script for its automated creation can be found under the \enquote{getting\_data} directory of our project code: \footnote{\url{https://github.com/imilas/Synths_Stacks_Search}}
\section{Details}
Our data sources are a large set of 2 second or shorter drum samples aggregated from personal libraries, free drum kits from the sample-swap project \footnote{https://sampleswap.org/} which we organized into 5 groups, and a large set of drum sounds aggregated from royalty free sources such as music radar \footnote{https://www.musicradar.com/}. We put together 3 databases of drums using these sources. We also created a database of synthetic noise from 1, 3, and 5 stacked virtual synthesizers. Specifications about our datasets can be found in tables~\ref{db:self},~\ref{db:radar},~\ref{db:sampleswap} and~\ref{db:noise}. We have made our dataset of free-drum sounds available for download. The scripts used to download and process royalty free samples are also made available. 

We prioritize making generalizable tools which can learn from and produce a variety of different sounds. We utilize these databases depending on the task at hand. At times, we merged or purged drum groups to simplify tasks.
\begin{table}[]
\centering
 \resizebox{\linewidth}{!}{\begin{tabular}{|l|l|l|l|l|l|l|l|l|l|}
\hline
DB Name & kick & snare & clap & tom\_high & tom\_mid & tom\_low & hihat\_closed &  hihat\_open & rim \\ \hline
MixedDB & 648 & 732 & 118 & 179 & 139 &  188 & 187 & 280 & 105 \\\hline
\end{tabular}}
\caption{Database 1: Mixed sources}
\label{db:self}
\end{table}

\begin{table}[]
\centering
\begin{tabular}{|l|l|l|l|l|l|l|l|l|}
\hline
DB Name & kick & snare & clap & tom & clap & hat & rim & shaker  \\ \hline
RadarDB & 1054 & 842   & 353 & 349 &  353 & 1561& 131 & 121 \\ \hline
\end{tabular}
\caption{Database 2: Royalty free sounds sourced from \enquote{Music Radar}}
\label{db:radar}
\end{table}

\begin{table}[]
\centering
\begin{tabular}{|l|l|l|l|l|l|}
\hline
 DB Name & kick & snare & clap & hat & other \\\hline
 FreeDB & 533 & 372 & 230 & 105 & 281 \\ \hline
\end{tabular}
\caption{Database 3: Free sounds sourced from the \enquote{Sample Swap} project. Simplified for our purposes. The version available for download contains more sample groups. The \enquote{other} category contains a variety of percussive sounds.}
\label{db:sampleswap}
\end{table}


\begin{table}[]
\centering
\begin{tabular}{|l|l|l|l|}
\hline
 Synth Noise Type & 1 Stack & 3 Stacks  & 5 Stacks \\ \hline
 Number of Examples & 2000 & 2000 & 2000 \\ \hline
\end{tabular}
\caption{Database of random noise examples from our virtual synthesizers}
\label{db:noise}
\end{table}


\end{document}